### 2022-04-26 README.Rmd
add cycling plans in LMA - readme
maybe too heavy to show. pointo to map with url.

<!-- todo: include shape of transport hubs in releases -->

@@

<!-- figs not showing on pkgdown -->

@@

>>>>

@@

@@

Compare the modeled cycling networks (segments overlapping) with expansion plans, by municipality.

<!-- todo: this is too heavy -->

```{r echo=FALSE, message=FALSE, warning=FALSE}
planned_network = sf::st_read("https://github.com/U-Shift/biclar/releases/download/0.0.1/CyclingPlans2021.gpkg", quiet = TRUE)

existing_network = sf::st_read("https://github.com/U-Shift/biclar/releases/download/0.0.1/CyclingNetwork2021.gpkg", quiet = TRUE)

greens2 = c("#1A7832", "#AFD4A0") #color pal

library(tmap)
tmap_mode("view")
tm_layout(title = "Existing and planned cycling networkn in LMA", panel.show = T) +
  tm_add_legend("fill",
                labels = "Planned",
                col = "#E3879E",
                z = 3) +
tm_shape(planned_network) +
  tm_sf(lwd = 1.5,
        #   color = "pink",
        col = "#E3879E",
        lty = "dashed",
        alpha = 0.8 ,
        legend.show = T,
        title.col = "Planned") +
tm_shape(existing_network) +
  tm_sf(col = "Tipologia",
           lwd = 2.5,
           palette = greens2,
        title.col = "Existing by typology",
        popup.vars = c(
      "Município" = "Municipio",
      "Tipologia" = "Tipologia",
      "Função" = "Funcao",      
     "Sentido" = "Sentido", 
     "Comprimento" = "Lenght", 
     "ID" = "ID"
    ),
  )

```
